---
title: "p8105_hw4_pj2325"
author: "Pengfei Jiang"
date: "2017/10/27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The project lead will load and tidy the data for this problem. The original data file includes data in “wide” format: the post-natal days on which developmental landmarks are reached are stored in columns called PD_outcome. The project lead will convert these data to “long” format, using reasonable variable names and values.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(haven)
library(janitor)
library(ggridges)
library(ggthemes)
library(rnoaa)
library(stats)
library(ggplot2)
library(DT)
library(dplyr)
```

In this part, Mengqi Zhu (uni:mz2662) is my collaborator.

```{r message=FALSE, warning=FALSE}
pups_data <- read_csv("./data/FAS_pups.csv") %>%
  clean_names() %>%
  mutate(sex = factor(sex, labels = c("male", "female")))

pups_tidy_data <- gather(pups_data, key = PD_outcome, value = days, pd_ears: pd_walk) %>%
  na.omit()
```

```{r message=FALSE, warning=FALSE}

```